Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-10-03 SupportingInformation.Rmd
modified

@@

@@

<!--do a TL analysis on the data just created-->
```{r tl_analysis, echo=F, cache=T, cache.extra=list(kend.surrog,spea.surrog,mtime("TaylorsLawTools.R"),seed,mtime("copsurrognd.R"))}
source("copsurrognd.R")
source("TaylorsLawTools.R")

@@

kend.stats.res<-list()
kend.points.res<-list()
spea.stats.res<-list()
spea.points.res<-list()
for (counter in 1:length(kend.surrog)){
 ks<-kend.surrog[[counter]]
 ss<-spea.surrog[[counter]]
 kend.stats.res[[counter]]<-matrix(NA,6,numdat) # to keep spatial TL stats
 spea.stats.res[[counter]]<-matrix(NA,6,numdat)
 kend.points.res[[counter]]<-array(NA,c(N,2,numdat)) # to keep log(mu), log(var) of spatial TL as a dataframe
 spea.points.res[[counter]]<-array(NA,c(N,2,numdat))
 for (sc in 1:numdat){
   khold<-tl_stats(ks[,,sc])
   kend.stats.res[[counter]][,sc]<-khold$s.stats #spatial TL only
   rownames(kend.stats.res[[counter]])<-names(khold$s.stats)
   kend.points.res[[counter]][,,sc]<-as.matrix(khold$s.points)

@@

par(op)
dev.off()
#---------------------------------------------------
#prepare for plots coming below
s.lin<-cbind(kend.stats.res[[1]][1,],kend.stats.res[[2]][1,],kend.stats.res[[3]][1,],kend.stats.res[[4]][1,])
s.hom<-cbind(kend.stats.res[[1]][2,],kend.stats.res[[2]][2,],kend.stats.res[[3]][2,],kend.stats.res[[4]][2,])
s.rmse<-cbind(kend.stats.res[[1]][3,],kend.stats.res[[2]][3,],kend.stats.res[[3]][3,],kend.stats.res[[4]][3,])
s.int<-cbind(kend.stats.res[[1]][4,],kend.stats.res[[2]][4,],kend.stats.res[[3]][4,],kend.stats.res[[4]][4,])
s.slope<-cbind(kend.stats.res[[1]][5,],kend.stats.res[[2]][5,],kend.stats.res[[3]][5,],kend.stats.res[[4]][5,])
s.quadcoeff<-cbind(kend.stats.res[[1]][6,],kend.stats.res[[2]][6,],kend.stats.res[[3]][6,],kend.stats.res[[4]][6,])

pdf("./Results/taylorslaw_results/SpatialTL_6stats_kendall.pdf",height=3,width=18)
op<-par(mfrow=c(1,6),mar=c(4.2,5,1,1),mgp=c(3,1,0))
#***DAN: x axis needs to be redone to show the copula names used in the surrogates

@@

#plot s.quadcoeff distr for each set of surrogates
boxplot(s.slope , col=rainbow(4) , xlab="Copula family", ylab="Spatial TL quadratic coefficient", cex.axis=1.5,cex.lab=1.5,xaxt="n")
axis(1, at = c(1:4), x2, cex.axis=1.5)

@@

par(op)
dev.off()
#---------------------------------------------------
#prepare for plots coming below
s.lin<-cbind(spea.stats.res[[1]][1,],spea.stats.res[[2]][1,],spea.stats.res[[3]][1,],spea.stats.res[[4]][1,])
s.hom<-cbind(spea.stats.res[[1]][2,],spea.stats.res[[2]][2,],spea.stats.res[[3]][2,],spea.stats.res[[4]][2,])
s.rmse<-cbind(spea.stats.res[[1]][3,],spea.stats.res[[2]][3,],spea.stats.res[[3]][3,],spea.stats.res[[4]][3,])
s.int<-cbind(spea.stats.res[[1]][4,],spea.stats.res[[2]][4,],spea.stats.res[[3]][4,],spea.stats.res[[4]][4,])
s.slope<-cbind(spea.stats.res[[1]][5,],spea.stats.res[[2]][5,],spea.stats.res[[3]][5,],spea.stats.res[[4]][5,])
s.quadcoeff<-cbind(spea.stats.res[[1]][6,],spea.stats.res[[2]][6,],spea.stats.res[[3]][6,],spea.stats.res[[4]][6,])

pdf("./Results/taylorslaw_results/SpatialTL_6stats_spearman.pdf",height=3,width=18)
op<-par(mfrow=c(1,6),mar=c(4.2,5,1,1),mgp=c(3,1,0))
x2<-c("C", "N", "F", "SC")

@@

\begin{figure}[!h]
\textbf{ \hspace{3.4 cm} (A) \hspace{3.2 cm} (B) \hspace{3.2 cm} (C) \hspace{3.1 cm} (D)} \\
\vspace{-0.5 cm} 
\begin{center}
\includegraphics[width=16 cm]{./Results/taylorslaw_results/SpatialTL_CNFSC_kendall.pdf}\\
\end{center}
\textbf{ \hspace{2.8 cm} (E) \hspace{1.8 cm} (F) \hspace{1.8 cm} (G) \hspace{1.8 cm} (H) \hspace{1.6 cm} (I) \hspace{2 cm} (J)}\\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=16 cm]{./Results/taylorslaw_results/SpatialTL_6stats_kendall.pdf}
\caption[Spatial Taylor's Law results]{Spatial Taylor's Law results: log(spatial variance) vs. log(spatial mean) for $ns=10$ number of (A) Clayton, (B) Normal, (C) Frank, (D) Survival Clayton surrogates; (E) p-value for test of linearity, (F) p-value for test of homoskedasticity, (G) root mean square error, (H) intercept, (I) slope, (J) quadratic coefficient of regression line for first panel plot. \label{fig_spTL}}
\end{center}
\end{figure}

>>>>

```{r modelsel_and_npa_aphid_count_allsp, echo=F, cache=T, cache.extra=list(seed,data_aphid_count,mtime("FittingCopula_selective_loc.R"), mtime("vivj_matrix.R"),mtime("good_loclist.R"),mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"),mtime("NonParamStat.R"),mtime("CopulaFunctions.R"), mtime("CopulaFunctions_flexible.R"))}

set.seed(seed)
library(parallel)
source("FittingCopula_selective_loc.R")
RES_all_sp_aphid_count<-mclapply(X=c(1:20),FUN=RES_single_sp,d_allsp=data_aphid_count,
                                 families=c(1,3:10,13,14,16:20),level=0.05,data_pt_thrs=35,
                                 good_loc_given=F,good_loc=NA,mc.cores=3)
saveRDS(RES_all_sp_aphid_count,"./Results/fitting_results/RES_all_sp_aphid_count.RDS")

source("good_loclist.R")
source("NonParamStat.R")
resloc<-"./Results/stat_results/stat_aphid_count/"
longs<-c(-4.567,0.57,-3.069,-3.312,-2.637,-1.682,-2.763,-0.356,-3.454,0.427,0.939)
lats<-c(55.477,52.26,56.457,55.949,52.125,55.213,53.854,51.807,50.628,51.733,51.185)

stat_aphid_count_allsp<-vector("list",20)

for(sp in 1:20){
  nm<-paste("sp_",sp,sep="")
  resloc2<-paste(resloc,nm,sep="")
   if (!dir.exists(resloc2)){
    dir.create(resloc2)
  }
  good_loc<-good_loclist(d_allsp=data_aphid_count,sp=sp,data_pt_thrs=30)

  temp<-multcall(d_allsp=data_aphid_count,sp=sp,lats=lats,longs=longs,
                 pfname=paste(resloc2,"/","Sp_",sp,sep=''),good_loc=good_loc)
  stat_aphid_count_allsp[[sp]]<-temp
}
saveRDS(stat_aphid_count_allsp,paste(resloc,file="stat_aphid_count_all_sp.RDS",sep=''))

summary_aphid_count_allsp<-as.data.frame(matrix(NA,nrow=20,ncol=8))
colnames(summary_aphid_count_allsp)<-c("species","#LTmUT>0","#LTmUT<0","val_LTmUT>0","val_LTmUT<0",
                                     "CorlmCoru_mean_CI","PlmPu_mean_CI","D2umD2l_mean_CI")

for(sp in c(1:20)){
  #cat("sp=",sp,"\n")
  summary_aphid_count_allsp$species[sp]<-sp
  LTmUT<-(RES_all_sp_aphid_count[[sp]]$LTdep_AICw - RES_all_sp_aphid_count[[sp]]$UTdep_AICw) # total loc pair 182
  summary_aphid_count_allsp$`#LTmUT>0`[sp]<-sum(LTmUT>0,na.rm=T)
  summary_aphid_count_allsp$`#LTmUT<0`[sp]<-sum(LTmUT<0,na.rm=T)
  ind_LTmUT_pos<-which(LTmUT>0,arr.ind = T)
  summary_aphid_count_allsp$`val_LTmUT>0`[sp]<-sum(LTmUT[ind_LTmUT_pos])
  ind_LTmUT_neg<-which(LTmUT<0,arr.ind = T)
  summary_aphid_count_allsp$`val_LTmUT<0`[sp]<-sum(LTmUT[ind_LTmUT_neg])

  summary_aphid_count_allsp$CorlmCoru_mean_CI[sp]<-list(
    c(unname(round(stat_aphid_count_allsp[[sp]]$numericdf[9,c(2:4)],3))))
  summary_aphid_count_allsp$PlmPu_mean_CI[sp]<-list(
    c(unname(round(stat_aphid_count_allsp[[sp]]$numericdf[10,c(2:4)],3))))
  summary_aphid_count_allsp$D2umD2l_mean_CI[sp]<-list(
    c(unname(round(stat_aphid_count_allsp[[sp]]$numericdf[11,c(2:4)],3))))
}
saveRDS(summary_aphid_count_allsp,"./Results/summary_aphid_count_allsp.RDS")
```

@@

\newpage
<!--results='hide'-->
```{r skewness_aphidcount_allsp_plot, echo=F, results="hide", warning=F, cache=T, cache.extra=list(seed,data_aphid_count,mtime("good_loclist.R"),mtime("skewness_multivar_dataset.R"),mtime("ncsurrog.R"),mtime("SkewnessAnd3CentMom.R"))}

# For sp =1, sp=4 and sp=6 : kendall preserving surrogates gives warning : Error in ncsurrog: ncov is not positive semidefinite : you can see those msg by deleting results="hide" and warning=F option in r chunk

numsurrog<-10000

splist<-c(1:20)
skw_aphid_count_spearman<-as.data.frame(matrix(NA,nrow=length(splist),ncol=3))
colnames(skw_aphid_count_spearman)<-c("realskw","p_left","p_right")
rownames(skw_aphid_count_spearman)<-paste("sp",splist,sep="")
pdf("./Results/skewness_results/skewness_aphid_count/aphid_count_allsp_skewness_spearman.pdf",height=20,width=20)
op<-par(mfrow=c(4,5),mar=c(4.2,5,1,1),mgp=c(3,1,0))
cat("Now for spearman preserving surrogs : aphid count","\n")
for(i in splist){
  cat("sp=",i,"\n")
  loclist<-good_loclist(d_allsp=data_aphid_count,sp=i,data_pt_thrs=30)
  ans<-skewness_testing(ts_matrix=sp_data(sp=i,d_allsp=data_aphid_count),loclist=loclist,
                        numsurrog=numsurrog,
                        ploton=T,
                        corpres="spearman") 
  p_left<-sum(ans$surrogskw < ans$realskw)/numsurrog
  p_right<-sum(ans$surrogskw > ans$realskw)/numsurrog
  skw_aphid_count_spearman$realskw[i]<-ans$realskw
  skw_aphid_count_spearman$p_left[i]<-p_left
  skw_aphid_count_spearman$p_right[i]<-p_right
  mtext(paste0("sp = ",i,", p_left = ",p_left,", p_right = ",p_right),side=3,line=-0.5,col="navyblue",cex = 1)
}
par(op)
dev.off()
saveRDS(skw_aphid_count_spearman,"./Results/skewness_results/skewness_aphid_count/skw_aphid_count_spearman.RDS")

skw_aphid_count_kendall<-as.data.frame(matrix(NA,nrow=length(splist),ncol=3))
colnames(skw_aphid_count_kendall)<-c("realskw","p_left","p_right")
rownames(skw_aphid_count_kendall)<-paste("sp",splist,sep="")
pdf("./Results/skewness_results/skewness_aphid_count/aphid_count_allsp_skewness_kendall.pdf",height=20,width=20)
op<-par(mfrow=c(4,5),mar=c(4.2,5,1,1),mgp=c(3,1,0))
cat("Now for kendall preserving surrogs : aphid count","\n")
for(i in splist){
  cat("sp=",i,"\n")
  loclist<-good_loclist(d_allsp=data_aphid_count,sp=i,data_pt_thrs=30)
  ans<-skewness_testing(ts_matrix=sp_data(sp=i,d_allsp=data_aphid_count),loclist=loclist,
                        numsurrog=numsurrog,
                        ploton=T,
                        corpres="kendall") 
  p_left<-sum(ans$surrogskw < ans$realskw)/numsurrog
  p_right<-sum(ans$surrogskw > ans$realskw)/numsurrog
  skw_aphid_count_kendall$realskw[i]<-ans$realskw
  skw_aphid_count_kendall$p_left[i]<-p_left
  skw_aphid_count_kendall$p_right[i]<-p_right
  mtext(paste0("sp = ",i,", p_left = ",p_left,", p_right = ",p_right),side=3,line=-0.5,col="navyblue",cex = 1)
}
par(op)
dev.off()
saveRDS(skw_aphid_count_kendall,"./Results/skewness_results/skewness_aphid_count/skw_aphid_count_kendall.RDS")
```

```{r skewness_aphidff_allsp_plot, echo=F, results="hide", warning=F, cache=T, cache.extra=list(seed,data_aphid_ff,mtime("good_loclist.R"),mtime("skewness_multivar_dataset.R"),mtime("ncsurrog.R"),mtime("SkewnessAnd3CentMom.R"))}

# For sp =12 and sp=16 : kendall preserving surrogates gives warning : Error in ncsurrog: ncov is not positive semidefinite : you can see those msg by deleting results="hide" and warning=F option in r chunk

numsurrog<-10000

splist<-c(1:20)
skw_aphid_ff_spearman<-as.data.frame(matrix(NA,nrow=length(splist),ncol=3))
colnames(skw_aphid_ff_spearman)<-c("realskw","p_left","p_right")
rownames(skw_aphid_ff_spearman)<-paste("sp",splist,sep="")
pdf("./Results/skewness_results/skewness_aphid_ff/aphid_ff_allsp_skewness_spearman.pdf",height=20,width=20)
op<-par(mfrow=c(4,5),mar=c(4.2,5,1,1),mgp=c(3,1,0))
cat("Now for spearman preserving surrogs : aphid ff","\n")
for(i in splist){
  cat("sp=",i,"\n")
  loclist<-good_loclist(d_allsp=data_aphid_ff,sp=i,data_pt_thrs=30)
  ans<-skewness_testing(ts_matrix=sp_data(sp=i,d_allsp=data_aphid_ff),loclist=loclist,
                        numsurrog=numsurrog,
                        ploton=T,
                        corpres="spearman") 
  p_left<-sum(ans$surrogskw < ans$realskw)/numsurrog
  p_right<-sum(ans$surrogskw > ans$realskw)/numsurrog
  skw_aphid_ff_spearman$realskw[i]<-ans$realskw
  skw_aphid_ff_spearman$p_left[i]<-p_left
  skw_aphid_ff_spearman$p_right[i]<-p_right
  mtext(paste0("sp = ",i,", p_left = ",p_left,", p_right = ",p_right),side=3,line=-0.5,col="navyblue",cex = 1)
}
par(op)
dev.off()
saveRDS(skw_aphid_ff_spearman,"./Results/skewness_results/skewness_aphid_ff/skw_aphid_ff_spearman.RDS")

skw_aphid_ff_kendall<-as.data.frame(matrix(NA,nrow=length(splist),ncol=3))
colnames(skw_aphid_ff_kendall)<-c("realskw","p_left","p_right")
rownames(skw_aphid_ff_kendall)<-paste("sp",splist,sep="")
pdf("./Results/skewness_results/skewness_aphid_ff/aphid_ff_allsp_skewness_kendall.pdf",height=20,width=20)
op<-par(mfrow=c(4,5),mar=c(4.2,5,1,1),mgp=c(3,1,0))
cat("Now for kendall preserving surrogs : aphid ff","\n")
for(i in splist){
  cat("sp=",i,"\n")
  loclist<-good_loclist(d_allsp=data_aphid_ff,sp=i,data_pt_thrs=30)
  ans<-skewness_testing(ts_matrix=sp_data(sp=i,d_allsp=data_aphid_ff),loclist=loclist,
                        numsurrog=numsurrog,
                        ploton=T,
                        corpres="kendall") 
  p_left<-sum(ans$surrogskw < ans$realskw)/numsurrog
  p_right<-sum(ans$surrogskw > ans$realskw)/numsurrog
  skw_aphid_ff_kendall$realskw[i]<-ans$realskw
  skw_aphid_ff_kendall$p_left[i]<-p_left
  skw_aphid_ff_kendall$p_right[i]<-p_right
  mtext(paste0("sp = ",i,", p_left = ",p_left,", p_right = ",p_right),side=3,line=-0.5,col="navyblue",cex = 1)
}
par(op)
dev.off()
saveRDS(skw_aphid_ff_kendall,"./Results/skewness_results/skewness_aphid_ff/skw_aphid_ff_kendall.RDS")
```

```{r skewness_plankton_allsp_plot, echo=F, results="hide", cache=T, cache.extra=list(seed,data_plankton_north_sea,mtime("good_loclist.R"),mtime("skewness_multivar_dataset.R"),mtime("ncsurrog.R"),mtime("SkewnessAnd3CentMom.R"))}

# There is no error msg or warning coming from ncsurrog : ncov semidefinite matrix for any species with spearman
# or kendall preserving surrogates.

splist<-c(1:22)
skw_plankton_spearman<-as.data.frame(matrix(NA,nrow=length(splist),ncol=3))
colnames(skw_plankton_spearman)<-c("realskw","p_left","p_right")
rownames(skw_plankton_spearman)<-paste("sp",splist,sep="")
skw_plankton_kendall<-skw_plankton_spearman
pdf("./Results/skewness_results/skewness_plankton_north_sea/plankton_allsp_skewness_spearman.pdf",height=24,width=24)
op<-par(mfrow=c(4,6),mar=c(4.2,5,1,1),mgp=c(3,1,0))
#cat("Now for spearman preserving surrogs : pns","\n")
for(i in splist){
  #cat("sp=",i,"\n")
  loclist<-good_loclist(d_allsp=data_plankton_north_sea,sp=i,data_pt_thrs=45)
  ans<-skewness_testing(ts_matrix=sp_data(sp=i,d_allsp=data_plankton_north_sea),loclist=loclist,
                        numsurrog=numsurrog,
                        ploton=T,
                        corpres="spearman") 
  p_left<-sum(ans$surrogskw < ans$realskw)/numsurrog
  p_right<-sum(ans$surrogskw > ans$realskw)/numsurrog
  skw_plankton_spearman$realskw[i]<-ans$realskw
  skw_plankton_spearman$p_left[i]<-p_left
  skw_plankton_spearman$p_right[i]<-p_right
  mtext(paste0("sp = ",i,", p_left = ",p_left,", p_right = ",p_right),side=3,line=-0.5,col="navyblue",cex = 1)
}
par(op)
dev.off()
saveRDS(skw_plankton_spearman,"./Results/skewness_results/skewness_plankton_north_sea/skw_plankton_spearman.RDS")

pdf("./Results/skewness_results/skewness_plankton_north_sea/plankton_allsp_skewness_kendall.pdf",height=20,width=20)
op<-par(mfrow=c(4,5),mar=c(4.2,5,1,1),mgp=c(3,1,0))
#cat("Now for kendall preserving surrogs : pns","\n")
for(i in splist){
  #cat("sp=",i,"\n")
  loclist<-good_loclist(d_allsp=data_plankton_north_sea,sp=i,data_pt_thrs=45)
  ans<-skewness_testing(ts_matrix=sp_data(sp=i,d_allsp=data_plankton_north_sea),loclist=loclist,
                        numsurrog=numsurrog,
                        ploton=T,
                        corpres="kendall") 
  p_left<-sum(ans$surrogskw < ans$realskw)/numsurrog
  p_right<-sum(ans$surrogskw > ans$realskw)/numsurrog
  skw_plankton_kendall$realskw[i]<-ans$realskw
  skw_plankton_kendall$p_left[i]<-p_left
  skw_plankton_kendall$p_right[i]<-p_right
  mtext(paste0("sp = ",i,", p_left = ",p_left,", p_right = ",p_right),side=3,line=-0.5,col="navyblue",cex = 1)
}
par(op)
dev.off()
saveRDS(skw_plankton_kendall,"./Results/skewness_results/skewness_plankton_north_sea/skw_plankton_kendall.RDS")
```

@@

<!--do a TL analysis on the data just created-->
```{r tl_analysis, echo=F, cache=T, cache.extra=list(kend.surrog,spea.surrog,mtime("mncurvat.R"),mtime("TaylorsLawTools.R"),seed,mtime("copsurrognd.R"))}
source("copsurrognd.R")
source("TaylorsLawTools.R")

@@

kend.stats.res<-list()
kend.points.res<-list()
spea.stats.res<-list()
spea.points.res<-list()
for (counter in 1:length(kend.surrog)){
 ks<-kend.surrog[[counter]]
 ss<-spea.surrog[[counter]]
 kend.stats.res[[counter]]<-matrix(NA,7,numdat) # to keep spatial TL stats
 spea.stats.res[[counter]]<-matrix(NA,7,numdat)
 kend.points.res[[counter]]<-array(NA,c(N,2,numdat)) # to keep log(mu), log(var) of spatial TL as a dataframe
 spea.points.res[[counter]]<-array(NA,c(N,2,numdat))
 for (sc in 1:numdat){
   khold<-tl_stats(ks[,,sc])
   kend.stats.res[[counter]][,sc]<-khold$s.stats #spatial TL only
   rownames(kend.stats.res[[counter]])<-names(khold$s.stats)
   kend.points.res[[counter]][,,sc]<-as.matrix(khold$s.points)

@@

par(op)
dev.off()
#---------------------------------------------------
#prepare for plots coming below
s.lin<-cbind(kend.stats.res[[1]][1,],kend.stats.res[[2]][1,],kend.stats.res[[3]][1,],kend.stats.res[[4]][1,])
s.hom<-cbind(kend.stats.res[[1]][2,],kend.stats.res[[2]][2,],kend.stats.res[[3]][2,],kend.stats.res[[4]][2,])
s.rmse<-cbind(kend.stats.res[[1]][3,],kend.stats.res[[2]][3,],kend.stats.res[[3]][3,],kend.stats.res[[4]][3,])
s.int<-cbind(kend.stats.res[[1]][4,],kend.stats.res[[2]][4,],kend.stats.res[[3]][4,],kend.stats.res[[4]][4,])
s.slope<-cbind(kend.stats.res[[1]][5,],kend.stats.res[[2]][5,],kend.stats.res[[3]][5,],kend.stats.res[[4]][5,])
s.quadcoeff<-cbind(kend.stats.res[[1]][6,],kend.stats.res[[2]][6,],kend.stats.res[[3]][6,],kend.stats.res[[4]][6,])
s.mncurv<-cbind(kend.stats.res[[1]][7,],kend.stats.res[[2]][7,],kend.stats.res[[3]][7,],kend.stats.res[[4]][7,])

pdf("./Results/taylorslaw_results/SpatialTL_7stats_kendall.pdf",height=3,width=21)
op<-par(mfrow=c(1,7),mar=c(4.2,5,1,1),mgp=c(3,1,0))
#***DAN: x axis needs to be redone to show the copula names used in the surrogates

@@

#plot s.quadcoeff distr for each set of surrogates
boxplot(s.quadcoeff , col=rainbow(4) , xlab="Copula family", ylab="Spatial TL quadratic coefficient", cex.axis=1.5,cex.lab=1.5,xaxt="n")
axis(1, at = c(1:4), x2, cex.axis=1.5)

#plot s.mncurv distr for each set of surrogates
boxplot(s.mncurv , col=rainbow(4) , xlab="Copula family", ylab="Spatial TL mean curvature", cex.axis=1.5,cex.lab=1.5,xaxt="n")
axis(1, at = c(1:4), x2, cex.axis=1.5)

@@

par(op)
dev.off()
#---------------------------------------------------
#prepare for plots coming below
s.lin<-cbind(spea.stats.res[[1]][1,],spea.stats.res[[2]][1,],spea.stats.res[[3]][1,],spea.stats.res[[4]][1,])
s.hom<-cbind(spea.stats.res[[1]][2,],spea.stats.res[[2]][2,],spea.stats.res[[3]][2,],spea.stats.res[[4]][2,])
s.rmse<-cbind(spea.stats.res[[1]][3,],spea.stats.res[[2]][3,],spea.stats.res[[3]][3,],spea.stats.res[[4]][3,])
s.int<-cbind(spea.stats.res[[1]][4,],spea.stats.res[[2]][4,],spea.stats.res[[3]][4,],spea.stats.res[[4]][4,])
s.slope<-cbind(spea.stats.res[[1]][5,],spea.stats.res[[2]][5,],spea.stats.res[[3]][5,],spea.stats.res[[4]][5,])
s.quadcoeff<-cbind(spea.stats.res[[1]][6,],spea.stats.res[[2]][6,],spea.stats.res[[3]][6,],spea.stats.res[[4]][6,])
s.mncurv<-cbind(spea.stats.res[[1]][7,],spea.stats.res[[2]][7,],spea.stats.res[[3]][7,],spea.stats.res[[4]][7,])

pdf("./Results/taylorslaw_results/SpatialTL_7stats_spearman.pdf",height=3,width=21)
op<-par(mfrow=c(1,7),mar=c(4.2,5,1,1),mgp=c(3,1,0))
x2<-c("C", "N", "F", "SC")

@@

\begin{figure}[!h]
\textbf{ \hspace{3.4 cm} (A) \hspace{3.2 cm} (B) \hspace{3.2 cm} (C) \hspace{3.1 cm} (D)} \\
\vspace{-0.5 cm} 
\begin{center}
\includegraphics[width=16 cm]{./Results/taylorslaw_results/SpatialTL_CNFSC_kendall.pdf}\\
\end{center}
\textbf{ \hspace{2.8 cm} (E) \hspace{1.8 cm} (F) \hspace{1.8 cm} (G) \hspace{1.8 cm} (H) \hspace{1.6 cm} (I) \hspace{2 cm} (J)}\\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=16 cm]{./Results/taylorslaw_results/SpatialTL_7stats_spearman.pdf}
\caption[Spatial Taylor's Law results]{Spatial Taylor's Law results: log(spatial variance) vs. log(spatial mean) for $ns=10$ number of (A) Clayton, (B) Normal, (C) Frank, (D) Survival Clayton surrogates; (E) p-value for test of linearity, (F) p-value for test of homoskedasticity, (G) root mean square error, (H) intercept, (I) slope, (J) quadratic coefficient of regression line for first panel plot. \label{fig_spTL}}
\end{center}
\end{figure}
